\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage[linktocpage=true]{hyperref}

\usepackage{mathpazo}

\begin{document}
\begin{titlepage}
	\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
    \begin{center}
            
    	\textsc{\LARGE Alabama Liquid Snake}\\[0.8cm]
    	\textsc{\Large University of Pretoria}\\[0.5cm]
    	\textsc{\large Epi-Use}\\[0.5cm]
    
    	\HRule\\[0.4cm]
    	
    	{\huge\bfseries Botic - Privacy aware chatbot}\\[0.2cm]
    	
    	{\huge User Manual}\\[0.2cm]

    	\HRule\\[0.5cm]

	    \textsc{Justin Grenfell} - u16028440 \\[0cm]
	    \textsc{Peter Msimanga} - u13042352 \\[0cm]
	    \textsc{Alicia Mulder} - u14283124 \\[0cm]
	    \textsc{Kyle Gaunt} - u15330967 \\[0cm]
	    \textsc{Lesego Mabe} - u15055214 \\[0cm]
    
    \end{center}
\end{titlepage}
\tableofcontents
\newpage
\section{Introduction/System Overview}

\subsection{System Configuration}

\subsection{Installation}

\section {Getting Started}

\section{Using the System}

\section{Troubleshooting}
What follows is a list of possible error conditions that may occur during the deployment and/or usage of your Botic instance as well as a number of ways we recommend they be dealt with.

\subsection{Deployment}
\begin{itemize}
    \item \textbf{Software doesn't install:} Check that you meet all of the prerequisites and that none of the packages installed were corrupted. During the download process
    \item \textbf{Software doesn't run:} Check the dockerfile and the angular build to ensure that all of the necessary prerequisite packages were installed.    
    \item \textbf{API calls return errors during runtime:} Ensure that your deployment environment is configured to allow cross-origin http requests.
\end{itemize}

\subsection {Usage}
\begin{itemize}
        \item \textbf{Bot does not respond.} Check your connection and ensure that the communication port that BOTIC communicates on is exposed.
        \item\textbf{Bot is not highlighting information.} Check your connection to make sure information is being sent. Otherwise, ensure that your server is configured to allow BOTIC to make HTTP requests.
        \item \textbf{Bot is giving incoherent responses.}Check your training data as well as your information digest in to see if it is loaded correctly and that your model is properly trained.
\end{itemize}


    



\end{document}