\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
%%\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage[linktocpage=true]{hyperref}

%%Page layout
\usepackage[margin=2.0cm]{geometry}
\usepackage{bookmark}

%%Figures
\usepackage{float}

\usepackage{mathpazo}

%%Font and Numbers
\renewcommand*\rmdefault{dayrom}
\usepackage[T1]{fontenc}
\normalfont
\usepackage{enumitem}

%%Packages for Referrences
\usepackage{url}
\usepackage{etoolbox}
\patchcmd{\thebibliography}{\section*{\refname}}{}{}{}
\patchcmd{\thebibliography}{\addcontentsline{toc}{section}{\refname}}{}{}{}

%%Group Comments
\usepackage{verbatim}

\begin{document}
\renewcommand{\familydefault}{\sfdefault}
\begin{titlepage}
	\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
	\begin{center}
		            
		\textsc{\LARGE Alabama Liquid Snake}\\[0.8cm]
		\textsc{\Large University of Pretoria}\\[0.5cm]
		\textsc{\large Epi-Use}\\[0.5cm]
		    
		\HRule\\[0.4cm]
		    	
		{\huge\bfseries Botic - Privacy aware chatbot}\\[0.2cm]
		    	
		{\huge Coding Standards}\\[0.2cm]
		
		\HRule\\[0.5cm]
		
		\textsc{Justin Grenfell} - u16028440 \\[0cm]
		\textsc{Peter Msimanga} - u13042352 \\[0cm]
		\textsc{Alicia Mulder} - u14283124 \\[0cm]
		\textsc{Kyle Gaunt} - u15330967 \\[0cm]
		\textsc{Lesego Mabe} - u15055214 \\[0cm]
		    
	\end{center}
\end{titlepage}
\tableofcontents
\newpage
\section{Introduction}

This document is meant to contain all details regarding the coding standards used in the development of all subsystems.

\subsection{Required and optional Items}
\subsubsection{Naming Conventions}
\subsubsection{Layout Rules}

We will be using Standardjs as the JavaScript standard style for the frontend. Here are a few of our standards:
\begin{enumerate}
	\item 2 spaces – for indentation
	\item Single quotes for strings – except to avoid escaping
	\item No unused variables – this one catches tons of bugs!
	\item No semicolons – It's fine. Really!
	\item More details
	\item Space after keywords if (condition) { ... }
	\item Space after function name function name (arg) { ... }
	\item Always use === instead of == – but obj == null is allowed to check null || undefined.
	\item Always handle the node.js err function parameter
	\item Declare browser globals with /* global */ comment at top of file. Prevents accidental use of vaguely-named browser globals like open, length, event, and name. Example: /* global alert, prompt */ Exceptions are: window, document, and navigator
\end{enumerate}

\end{document}